---
title: "Presentation"
author: "Group 3"
date: "10/27/2021"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    highlight: pygments
---
<style type="text/css">
p { text-align: left; }
</style>

```{r setup,echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set( include=FALSE, echo=FALSE, message=FALSE, warning=FALSE)
pacman::p_load("tidyverse","ggplot2","dplyr","png")
source("wrangling.R")
source("figure_functions.R")
```

# Possible Questions:  
1.Does the use of potentially human toxic chemicals vary between states?  
2.Does the use of potentially bee toxic chemicals vary between states?    
3.How Pesticide dosage changes by years and states?    

# Proportions for each state
```{r, include = TRUE}
state_fig()
```

# Maps of Strawberries Yield
```{r, include = TRUE}
map.straw(df.lb, "Strawberries Yield(in LB)\n2016 2018 2019")
#map.straw(df.app, "Strawberries Yield(LB/ACRE/APPLICATION)\n2016 2018 2019")
#map.straw(df.year, "Strawberries Yield(LB/ACRE/YEAR)\n2016 2018 2019")
```
```{r}
map.straw(df.num,"Strawberries Yield(NUMBER)\n2016 2018 2019")
#map.straw(df.PCT, "Strawberries Yield(PCT OF AREA BEARING)\n2016 2018 2019") 
```

# Applications of Bee Toxins
```{r, include = TRUE,warning=FALSE,results = FALSE}
bee_tox()
```

# Applications of Carcinogens
```{r,include = TRUE,warning=FALSE,results = FALSE}
carc_apps()
```

# Comparison of Toxicities and Application
```{r,include = TRUE}
group_bars()
```


# Conclusions
```{r,include = TRUE}
```
