---
title: "Strawberry Presentation"
author: "Group 3: Rose Determan, Yongrong Chai, Wuji Shan, Tong Sun"
date: "11/3/2021"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    highlight: pygments
---
<style type="text/css">
p { text-align: left; }
</style>

```{r setup,echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set( include=FALSE, echo=FALSE, message=FALSE, warning=FALSE)
pacman::p_load("tidyverse","ggplot2","dplyr","png")
source("wrangling.R")
source("figure_functions.R")
```

# Possible Questions:  
1.How does the strawberry yield vary between states and years?  
2.Is there any relationship between Level of Bee Toxicity and Carcinogen Level?

# Proportions for each state
```{r, include = TRUE}
state_fig()
```

# Maps of Strawberries Yield in CWT/Acre
```{r, include = TRUE}
map.straw(strawb_yield[strawb_yield$Data.Item == "STRAWBERRIES - YIELD, MEASURED IN CWT / ACRE",], "Strawberries Yield (CWT/Acre))\n2015-2020")
#map.straw(df.app, "Strawberries Yield(LB/ACRE/APPLICATION)\n2016 2018 2019")
#map.straw(df.year, "Strawberries Yield(LB/ACRE/YEAR)\n2016 2018 2019")
```

# Maps of Pesticide Applications
```{r, include = TRUE}
map.straw(df.num,"Average Number of Pesticide Applications \n2016 2018 2019")
#map.straw(df.PCT, "Strawberries Yield(PCT OF AREA BEARING)\n2016 2018 2019") 
```

```{r, include = F,warning=FALSE,results = FALSE}
# Applications of Bee Toxins
bee_tox()
```

```{r,include = F,warning=FALSE,results = FALSE}
# Applications of Carcinogens
carc_apps()
```

# Comparison of Toxicities and Application


```{r,include = TRUE,fig.width = 11.2,fig.height = 6}
group_bars()
```

# Conclusions:
1.From the bin plot, we can see that the proportions of strawberries numbers have a significant difference between states. California has the largest share and Washington has the smallest.  
2.From the bar chart, we can see that all strawberries measured in number with toxicity_bee exist with slight level of carcinogen.There does not exist strawberries measured in number with toxicity_bee in the 2 and 3 level of carcinogen.  
